The Leaky Semicolon (Supplementary Material)

### 2021-11-10 paper/tool.tex
pass through 8

We have run \PwTer{} over the Java Causality Tests~\cite{PughWebsite} supported in the input syntax, and tabulated the results in Table~\ref{fig:tool}.
For context, we have included the results of \MRD{} for the Java Causality tests~\cite{DBLP:conf/esop/PaviottiCPWOB20}.
Note that \MRD{} and \MRDRC{} do not give the correct outcome on jctc17--18---the reason is that local invariant reasoning in \MRD{} is too constrained (see \textsection\ref{sec:lir}).

>>>>

We have run \PwTer{} over the Java Causality Tests~\cite{PughWebsite} supported in the input syntax, and tabulated the results in Table~\ref{fig:tool}.
For context, we have included the results of \MRD{} for the Java Causality tests~\cite{DBLP:conf/esop/PaviottiCPWOB20}.
Note that \MRD{} and \MRDRC{} do not give the correct outcome on TC17--18---the reason is that local invariant reasoning in \MRD{} is too constrained (see \textsection\ref{sec:lir}).
